A complete solution for scattering in a kind of quiver gauge theory

### 2025-04-14 Intermediate report/main.tex
New

\documentclass{beamer}
\usetheme{Madrid}
\usefonttheme{professionalfonts}
\usecolortheme{rose}
\usepackage{fontspec}
\setmainfont{Times New Roman}
\usepackage{amsmath}
\usepackage{bm}
\usepackage{booktabs}
\usepackage{tikz}
\usepackage{svg}
\usepackage{graphics}
\usepackage{appendixnumberbeamer}
\usepackage{mathtools}
\usepackage{enumitem}
\usepackage{subcaption}
\usepackage{comment}
\usepackage[most]{tcolorbox}
\tcbset{
  thickitembox/.style={
    colback=white,
    colframe=white,
    left=2mm,
    before skip=4pt,
    after skip=4pt,
    borderline west={3pt}{0pt}{gray},  % ← 这里控制线条粗细和颜色
    enhanced,
  }
}
\setlist[itemize]{label=\textbullet}
\usetikzlibrary{decorations.pathreplacing}
\usetikzlibrary{arrows.meta}
\setlength{\parskip}{0.3em}
\newcommand{\aket}[1]{|#1\rangle}
\newcommand{\sket}[1]{|#1]}
\newcommand{\avg}[1]{\langle #1 \rangle}
\newcommand{\mdavg}[2]{\langle #1 \rangle\!\langle #2 \rangle}
\AtBeginSection[]{
\begin{frame} 
    \frametitle{Contents}
    \tableofcontents[currentsection]
\end{frame}
}
\title[Application of BCFW]{A complete solution for scattering in a kind of quiver gauge theory}
\author{Su Yingze}
\institute{Nagoya University}
\date[4 21st 2025]{April 21st 2025}

@@

    Here we consider the case in which all particles are massless, $p_i^2 = 0$ for all $i = 1, 2, \dotsc, n$. Then introduce $n$ complex-valued vectors $r_i^\mu$.
    \begin{enumerate}[label=(\roman*)]
        \item $\sum_{i=1}^n r_i^\mu=0$,
        \item $r_i\cdot r_j = 0$ for all $i,j=1, 2, \ldots, n.$ In particular $r_i^2=0$,
        \item $p_i \cdot r_i =0$ for each i (no sum). 
    \end{enumerate}

These vectors $r_i$ are used to define n shifted momenta
\begin{equation*}
    \hat{p}_i^\mu \equiv p_i^\mu + zr_i^\mu \qquad \text{with} z \in \mathcal{C}
\end{equation*}
Then, $\hat{P}_I^2$ is \textcolor{red}{linear} in z:
\begin{equation*}
    \hat{P}_I^2=\left(\sum_{i\in I} \hat{p}_i \right) ^2 = P_I^2 +2zP_I\cdot R_I \quad \text{with} \quad R_I=\sum_{i\in I} r_i ,
\end{equation*}

\end{frame}
\begin{frame}
Note that,
    \begin{enumerate}[label=(\Alph*)]
    \item By property (i), momentum conservation holds for the shifted momenta: $\sum_{i=1}^{n} \hat{p}_i^\mu =0$,
    \item By (ii) and (iii), we have $\hat{p}_i^2=0$, so each shifted momentum is on-shell,
    \item For a non-trival subset of generic momenta $\{p_i\}_{i\in I}$, define $P_I^\mu=\sum_{i\in I}p_i^\mu$.
    \end{enumerate}
Then, $\hat{P}_I^2$ is \textcolor{red}{linear} in z:
\begin{equation*}
    \hat{P}_I^2=\left(\sum_{i\in I} \hat{p}_i \right) ^2 = P_I^2 +2zP_I\cdot R_I \quad \text{with} \quad R_I=\sum_{i\in I} r_i ,
\end{equation*}
because the $z^2$ term vanishes by property (ii). We can write 
\begin{equation*}
    \hat{P}_I^2 = -\frac{P_I^2}{z_I}(z-z_I) \quad \text{with} \quad z_I=-\frac{P_I^2}{2P_I\cdot R_I}
\end{equation*}
\end{frame}
\begin{frame}
    \frametitle{Fantasitic result from Cauchy Theorem}
    As a result of (A) and (B) (momentum conservation and on-shell), we can consider amplitude $A_n$ in terms of shifted momentum $\hat{p}_i^\mu$ instead of
    original real momentum. 
    \begin{equation*}
        A_n \longrightarrow \hat{A}_n(z)
    \end{equation*}
    and we have known the possible positions of single poles, $z_I$, different propagators give 
    us different single poles in the z-plane. 
    \par
    If we consider the meromorphic function $\frac{\hat{A}_n(z)}{z}$ in the complex plane, pick a contour that surrounds the simple pole at the origin. 
    \textcolor{red}{$\bigstar$ The most important point here is that}
    \begin{equation*}
        \boxed{\color{red}\mathrm{Res}|_{z=0}\frac{\hat{A}_n(z)}{z}=\hat{A}_n(0)=A_n}
    \end{equation*}
    It means that the original amplitude equals to the residue at origin.
\end{frame}
\begin{frame}
    From Cauchy Theorem, we can ontain
    \begin{equation*}
        A_n=-\sum_{z_I}Res|_{z=z_I}\frac{\hat{A}_n(z)}{z}+B_n,
    \end{equation*}
    where $B_n$ is the residue of the pole at $z=\infty$, called boundary term.

@@

\begin{frame}
\frametitle{Spinor-helicity formalism}
    The critical point for Spinor-helicity formalism is that a 4-vector $p_\mu$ in $(\frac{1}{2},\frac{1}{2})$ representation can be equivalently represented by a bispinor in $(\frac{1}{2},0)\bigoplus (0,\frac{1}{2})$ representation.
    Specifically
    \begin{itemize}
        \item $\bm{\text{Massless Case}}$\\
    \begin{equation*}
        p_\mu \sigma^\mu=p_{\alpha\dot{\alpha}}=\begin{pmatrix*} 
            p^0-p^3 & -p^1+ip^2\\
            -p^1-ip^2 & p^0+p^3
        \end{pmatrix*}
    \end{equation*}
    And $p_{\alpha\dot{\alpha}}$ can be decomposed into product of two Weyl spinors
    \begin{equation*}
        p_{\alpha\dot{\alpha}}=\lambda_\alpha \tilde{\lambda}_{\dot{\alpha}}=\aket{\lambda}[\lambda|
    \end{equation*}
    Here we can find that there is a ambiguity for the definition, the momentum is invariant under the following redefinition
    \begin{equation*}
        \lambda \rightarrow t^{-1}\lambda, \qquad \tilde{\lambda}\rightarrow t\tilde{\lambda}, \qquad t\in\mathbb{C^*} 
    \end{equation*}
    same as 
    \begin{equation*}
        \aket{\lambda}\rightarrow t^{-1}\aket{\lambda}, \qquad \sket{\lambda}\rightarrow t\sket{\lambda}
    \end{equation*}
    \end{itemize}
\end{frame}

@@

    In the language of field theories, quiver gauge theories contain gauge fields and fermions, summarized in a pictotial representaion.
    \begin{figure}
        \centering
        \begin{minipage}{0.45\textwidth}
            \centering
            \includegraphics[width=0.6\textwidth]{Moosed.jpeg}
            \caption*{Moose diagram}
        \end{minipage}
        \hspace{1em}
        \begin{minipage}{0.3\textwidth}
            \begin{gather*}
                N-\text{sided polygon}\\
                G: \text{gauge group} \quad SU(m)\\
                \rightarrow : \text{Unitary scalar fields}\quad \Phi_{ij} 
            \end{gather*}
        \end{minipage}

    \end{figure}
\end{frame}
\begin{frame}
    \frametitle{Why we foucs on quiver gauge theory?}
    The lagrangian can be written like
    \begin{equation*}
        \mathcal{L}=-\sum_{i=1}^{N}\frac{1}{2}\mathrm{Tr}(F_i)^2+\sum_{i=1}^{k}\mathrm{Tr}[(D_\mu\Phi_i)^\dagger(D^\mu\Phi_i)],
    \end{equation*}
    here $F_i$ refers to the ith gauge field strength, scalar field $\Phi_i$ transformed under the \textcolor{red}{bi-fundamental} representation and the covariant derivative equals to
    \begin{equation*}
        D_\mu \Phi_i=\partial_\mu \Phi_i -ig_iV_{i\mu}\Phi_i+ig_{i+1}\Phi_i V_{i+1\mu}.
    \end{equation*}
    Here, gauge field and scalar field transformed like
    \begin{equation*}
        \bm{A_{i\mu}}\rightarrow g_i(x) \bm{A_{i\mu}} g_i^-(x),\qquad \Phi_i\rightarrow g_i(x)\Phi_i g_{i+1}^-(x)
    \end{equation*}
    It is easy to confirm that this theory is invariant under $\prod_1^N SU(M)$ gauge group.
\end{frame}
\begin{frame}
    It has been proposed that this model actually discretized a five-dimension gauge theory with gauge group $SU(m)$, where the 
    only the fifth dimension are latticed.
    \begin{itemize}
        \item If $SU(m)_1$ and $SU(m)_N$ are connected $\longrightarrow$ $S^2$ compactification
        \item If not connected $\longrightarrow$ $\mathrm{Interval}$ compactification
    \end{itemize}
    After higgsing, we can obtain a spectrum
    \begin{equation*}
        M_k^2=4g^2g_s^2\sin^2\left(\frac{\pi k}{N}\right)
    \end{equation*}
    This is precisely the \textcolor{red}{Kaluza-Klein} spectrum under $S^2$ compactification.
\end{frame}
\begin{frame}
    {What is relation to scattering amplitude?}
    The critical point is \textcolor{red}{locality}. 
    \begin{itemize}
        \item Space-Time Locality $\longrightarrow$ local field theories
        \item Theory Space Locality $\longrightarrow$ Discretized theory space
    \end{itemize}

@@

        % Text Node
        \draw (103,93.4) node [anchor=north west][inner sep=0.75pt]    {$G_{1}$};
        % Text Node
        \draw (142,94.4) node [anchor=north west][inner sep=0.75pt]    {$G_{2}$};
        % Text Node
        \draw (180,94.4) node [anchor=north west][inner sep=0.75pt]    {$G_{3}$};
        % Text Node
        \draw (220,94.4) node [anchor=north west][inner sep=0.75pt]    {$G_{4}$};
        % Text Node
        \draw (124,140.4) node [anchor=north west][inner sep=0.75pt]    {$\Phi _{1}$};
        % Text Node
        \draw (164,140.4) node [anchor=north west][inner sep=0.75pt]    {$\Phi _{2}$};
        % Text Node
        \draw (203,141.4) node [anchor=north west][inner sep=0.75pt]    {$\Phi _{3}$};
        \end{tikzpicture}
\end{center}
If we change this to a scattering diagram
\begin{figure}
    \centering
\begin{minipage}{0.4\textwidth}

@@

\end{minipage}
\hspace{1em}
\begin{minipage}{0.4\textwidth}
    \begin{equation*}
        \sim 1/z^{\textcolor{red}{\textcircled{\textcolor{black}{4}}}}
    \end{equation*}
\end{minipage}
\end{figure}
\end{frame}
\begin{frame}
    \frametitle{Classification of scattering amplitude}
    For the simplicity, we started front the two-site gauge theory, means that there are only two gauge fields $V_1$, $V_2$ and one scalar field $\Phi$, $\Phi^\dagger$.
    The amplitudes in this theory can be classified to many types
    \begin{columns}[T]
        \begin{column}{0.48\textwidth}
            \begin{itemize}
                \item 3-point
                    \begin{itemize}
                        \item $\bm{V_1\Phi\Phi^\dagger}$
                        \item $\bm{V_2\Phi\Phi^\dagger}$
                        \item $\bm{V_1V_1V_1}$
                        \item $\bm{V_2V_2V_2}$
                    \end{itemize}
            \end{itemize}
        \end{column}
        \begin{column}{0.48\textwidth}
            \begin{itemize}
                \item 4-point
                \begin{itemize}
                    \item $\bm{V_1V_1V_1V_1}$
                    \item $\bm{V_2V_2V_2V_2}$
                    \item $\bm{\Phi^\dagger V_1V_1\Phi}$
                    \item $\bm{\Phi V_2V_2\Phi^\dagger}$
                    \item $\bm{\Phi V_2 \Phi^\dagger V_1}$
                    \item $\bm{\Phi\Phi^\dagger\Phi\Phi^\dagger}$
                \end{itemize}
            \end{itemize}
        \end{column}
    \end{columns}
\end{frame}

\begin{frame}
    \begin{columns}[T]
        \begin{column}{0.6\textwidth}
        \begin{itemize}
            \item 5-point
            \begin{itemize}
                \item $\bm{V_1V_1V_1V_1V_1}$
                \item $\bm{V_2V_2V_2V_2V_2}$
                \item $\bm{\Phi^\dagger V_1V_1V_1\Phi}$
                \item $\bm{\Phi V_2V_2V_2\Phi^\dagger}$
                \item $\bm{V_2\Phi^\dagger V_1V_1\Phi}$
                \item $\bm{\Phi V_2V_2\Phi^\dagger V_1}$
                \item $\textcolor{red}{\Phi\Phi^\dagger\Phi\Phi^\dagger V_1}$ (Not yet solved)
                \item $\textcolor{red}{\Phi\Phi^\dagger\Phi\Phi^\dagger V_2}$ (Not yet solved)
            \end{itemize}
        \end{itemize}
    \end{column}
    \begin{column}{0.48\textwidth}
        \begin{itemize}
            \item 6-point
            \begin{itemize}
                \item $\bm{V_1V_1V_1V_1V_1V_1}$
                \item $\bm{V_2V_2V_2V_2V_2V_2}$
                \item $\bm{\Phi^\dagger V_1V_1V_1V_1\Phi}$
                \item $\bm{\Phi V_2V_2V_2V_2\Phi^\dagger}$
                \item $\bm{V_2V_2\Phi^\dagger V_1V_1\Phi}$
                \item $\bm{\Phi V_2V_2\Phi^\dagger V_1V_1}$\\
                $\qquad$ $\vdots$\\
                $\qquad$ $ \vdots$
            \end{itemize}
        \end{itemize}
    \end{column}
    \end{columns}
\end{frame}

\begin{frame}
    \frametitle{Color structure}
    \begin{itemize}
        \item n$ V_1$ or n$V_2$\\
        This part is completely the same as the pure gluon amplitude, so we can directly borrow the
        existing results.
        \begin{equation*}
            \boxed{\text{Parke - Talyor Formula}:\quad A[\cdots,i^-,\cdots,j^-,\cdots]=\frac{\avg{ij}^4}{\avg{12}\!\avg{23}\cdots\avg{n1}}}
        \end{equation*}
        \textcolor{red}{Notice that this formula only applies for MHV amplitudes, although the NMHV can be completely solved.}
    \end{itemize}
\end{frame}

@@

\begin{frame}
    \frametitle{OPP(Order preserving permutation)}
    From the 4 point case, we have known that the relative order between gauge boson 1 and gauge boson 2 does not affect the color structure. 
    Thus, it is necessary to introduce the \textbf{OPP(Order preserving permutation)}. For example:
    \begin{equation*}
        (3_1,4_1,5_2) \quad (3_1,5_2,4_1) \quad (5_2,3_1,4_1)
    \end{equation*}
    These three permutations are different OPP for $(3_1,4_1,5_2)$, so that give us the same color factor.
\end{frame}

\section{Scattering amplitudes from BCFW}
\begin{frame}
    \frametitle{Basic building block -- 3-point}
    From the previous section, we have known that there are only two kinds of 3 point amplitude
    \begin{gather*}
        A[1,2,3^+]=\frac{[23][31]}{[12]},\qquad A[1,2,3^-]=\frac{\avg{23}\!\avg{31}}{\avg{12}}\\
        A[3^+,4^+,5^-]=\frac{[34]^3}{[45][53]},\qquad A[3^-,4^-,5_+]=\frac{\avg{34}^3}{\avg{45}\!\avg{53}}
    \end{gather*}
    By using the 3 point building block, we can construct 4 point color-ordered amplitudes from BCFW recursion relation.
\end{frame}

>>>>

\documentclass{beamer}
\usetheme{Madrid}
\usefonttheme{professionalfonts}
\usecolortheme{rose}
\usepackage{fontspec}
\setmainfont{Times New Roman}
\usepackage{amsmath}
\usepackage{bm}
\usepackage{booktabs}
\usepackage{tikz}
\usepackage{svg}
\usepackage{graphics}
\usepackage{appendixnumberbeamer}
\usepackage{mathtools}
\usepackage{enumitem}
\usepackage{subcaption}
\usepackage{comment}
\usepackage[most]{tcolorbox}
\tcbset{
  thickitembox/.style={
    colback=white,
    colframe=white,
    left=2mm,
    before skip=4pt,
    after skip=4pt,
    borderline west={3pt}{0pt}{gray},  % ← 这里控制线条粗细和颜色
    enhanced,
  }
}
\setlist[itemize]{label=\textbullet}
\usetikzlibrary{decorations.pathreplacing}
\usetikzlibrary{arrows.meta}
\setlength{\parskip}{0.3em}
\newcommand{\aket}[1]{|#1\rangle}
\newcommand{\sket}[1]{|#1]}
\newcommand{\avg}[1]{\langle #1 \rangle}
\newcommand{\mdavg}[2]{\langle #1 \rangle\!\langle #2 \rangle}
\newcommand{\asqu}[1]{{\langle#1\rangle}^2}
\AtBeginSection[]{
\begin{frame} 
    \frametitle{Contents}
    \tableofcontents[currentsection]
\end{frame}
}
\title[Application of BCFW]{A complete solution for scattering in a kind of quiver gauge theory}
\author{Su Yingze}
\institute{Nagoya University}
\date[4 21st 2025]{April 21st 2025}

@@

    Here we consider the case in which all particles are massless, $p_i^2 = 0$ for all $i = 1, 2, \dotsc, n$. We choose two momentum to be shifted oppositely 
    \begin{equation*}
        p_i\rightarrow\hat{p}_i(z)\equiv p_i-zk,\qquad p_j\rightarrow\hat{p}_j(z)\equiv p_j+zk
    \end{equation*}
    satisfying 
    \begin{equation*}
        k^2=0,\qquad p_i\cdot k=0,\qquad p_j\cdot k=0
    \end{equation*}
    Note that,
    \begin{itemize}
        \item Momentum conservation holds for shifted momentum: $\sum_{i=1}^{n}\hat{p}_i^\mu=0$,
        \item Each shifted momentum is still on-shell: $\hat{p}_i^2=0$
        \item For a non-trival subset of generic momenta $\{p_i\}_{i\in I}$, define $P_I^\mu=\sum_{i\in I}p_i^\mu$, $\hat{P}_I^2$ is \textcolor{red}{linear} in z:
              \begin{equation*}
                \hat{P}_I^2=\left(\sum_{i\in I} \hat{p}_i \right) ^2 = P_I^2 -2zP_I\cdot k=-\frac{P_I^2}{z_I}(z-z_I) \quad \text{with} \quad z_I=\frac{P_I^2}{2P_I\cdot k}
              \end{equation*}
    \end{itemize}

\begin{frame}
    \frametitle{Fantasitic result from Cauchy Theorem}
    As a result, we can consider amplitude $A_n$ in terms of shifted momentum $\hat{p}_i^\mu$ instead of original real momentum. 
    \begin{equation*}
        A_n \longrightarrow \hat{A}_n(z)
    \end{equation*}
    and we have known the possible positions of single poles, $z_I$, different propagators give 
    us different single poles in the z-plane. 
    \par
    If we consider the meromorphic function $\frac{\hat{A}_n(z)}{z}$ in the complex plane, pick a contour that surrounds the simple pole at the origin. 
    \textcolor{red}{$\bigstar$ The most important point here is that}
    \begin{equation*}
        \boxed{\color{red}\mathrm{Res}|_{z=0}\frac{\hat{A}_n(z)}{z}=\hat{A}_n(0)=A_n}
    \end{equation*}
    It means that the original amplitude equals to the residue at origin.
\end{frame}
\begin{frame}
    From Cauchy Theorem, we can ontain
    \begin{equation*}
        A_n=-\sum_{z_I}\textrm{Res}|_{z=z_I}\frac{\hat{A}_n(z)}{z}+B_n,
    \end{equation*}
    where $B_n$ is the residue of the pole at $z=\infty$, called boundary term.

@@

\begin{frame}
\frametitle{Spinor-helicity formalism}
    The critical point for Spinor-helicity formalism is that a 4-vector $p_\mu$ in $(\frac{1}{2},\frac{1}{2})$ representation can be equivalently represented by a bispinor in $(\frac{1}{2},0)\bigoplus (0,\frac{1}{2})$ representation.
    Specifically
    \begin{itemize}
        \item $\bm{\text{Massless Case}}$\\
    \begin{equation*}
        p_\mu \sigma^\mu=p_{\alpha\dot{\alpha}}=\begin{pmatrix*} 
            p^0-p^3 & -p^1+ip^2\\
            -p^1-ip^2 & p^0+p^3
        \end{pmatrix*}
    \end{equation*}
    And $p_{\alpha\dot{\alpha}}$ can be decomposed into product of two Weyl spinors
    \begin{equation*}
        p_{\alpha\dot{\alpha}}=\lambda_\alpha \tilde{\lambda}_{\dot{\alpha}}=\aket{\lambda}[\lambda|
    \end{equation*}
    Here we can notice that there is an ambiguity for the definition, the momentum is invariant under the following redefinition
    \begin{equation*}
        \lambda \rightarrow t^{-1}\lambda, \qquad \tilde{\lambda}\rightarrow t\tilde{\lambda}, \qquad t\in\mathbb{C^*} 
    \end{equation*}
    same as 
    \begin{equation*}
        \aket{\lambda}\rightarrow t^{-1}\aket{\lambda}, \qquad \sket{\lambda}\rightarrow t\sket{\lambda}
    \end{equation*}
    \end{itemize}
\end{frame}

@@

    In the language of field theories, quiver gauge theories contain gauge fields and fermions, summarized in a pictotial representaion.
    \begin{figure}
        \centering
        \begin{minipage}{0.45\textwidth}
            \centering
            \includegraphics[width=0.6\textwidth]{Moosed.jpeg}
            \caption*{Moose diagram}
        \end{minipage}
        \hspace{1em}
        \begin{minipage}{0.3\textwidth}
            \begin{gather*}
                N\text{-sided polygon}\\
                G: \text{gauge group} \quad SU(m)\\
                \rightarrow : \text{Unitary scalar fields}\quad \Phi_{ij} 
            \end{gather*}
        \end{minipage}

    \end{figure}
\end{frame}
\begin{frame}
    \frametitle{Why we foucs on quiver gauge theory?}
    The lagrangian can be written like
    \begin{equation*}
        \mathcal{L}=-\sum_{i=1}^{N}\frac{1}{2}\mathrm{Tr}(F_i)^2+\sum_{i=1}^{k}\mathrm{Tr}[(D_\mu\Phi_i)^\dagger(D^\mu\Phi_i)],
    \end{equation*}
    here $F_i$ refers to the ith gauge field strength, scalar field $\Phi_i$ transformed under the \textcolor{red}{bi-fundamental} representation and the covariant derivative equals to
    \begin{equation*}
        D_\mu \Phi_i=\partial_\mu \Phi_i -ig_iA_{i\mu}\Phi_i+ig_{i+1}\Phi_i A_{i+1\mu}.
    \end{equation*}
    Here, gauge field and scalar field transformed like
    \begin{equation*}
        \bm{A_{i\mu}}\rightarrow g_i(x) \bm{A_{i\mu}} g_i^-(x),\qquad \Phi_i\rightarrow g_i(x)\Phi_i g_{i+1}^-(x)
    \end{equation*}
    It is easy to confirm that this theory is invariant under $\prod_1^N SU(m)$ gauge group.
\end{frame}
\begin{frame}
    It has been proposed that this model actually discretized a five-dimension gauge theory with gauge group $SU(m)$, where 
    only the fifth dimension are latticed.
    \begin{itemize}
        \item If $SU(m)_1$ and $SU(m)_N$ are connected $\longrightarrow$ $S^2$ compactification
        \item If not connected $\longrightarrow$ $\mathrm{Interval}$ compactification
    \end{itemize}
    After higgsing, we can obtain a spectrum
    \begin{equation*}
        M_k^2=4g^2g_s^2\sin^2\left(\frac{\pi k}{N}\right)
    \end{equation*}
    This is precisely the \textcolor{red}{Kaluza-Klein} spectrum under $S^2$ compactification.
\end{frame}
\begin{frame}
    {What is relation to scattering amplitude?}
    The critical point is \textcolor{red}{locality}. 
    \begin{itemize}
        \item Space-Time Locality $\longrightarrow$ local field theories
        \item Theory Space Locality $\longrightarrow$ Discretized theory space
    \end{itemize}

@@

        % Text Node
        \draw (103,93.4) node [anchor=north west][inner sep=0.75pt]    {$G_{1}$};
        % Text Node
        \draw (142,94.4) node [anchor=north west][inner sep=0.75pt]    {$G_{2}$};
        % Text Node
        \draw (180,94.4) node [anchor=north west][inner sep=0.75pt]    {$G_{3}$};
        % Text Node
        \draw (220,94.4) node [anchor=north west][inner sep=0.75pt]    {$G_{4}$};
        % Text Node
        \draw (124,140.4) node [anchor=north west][inner sep=0.75pt]    {$\Phi _{1}$};
        % Text Node
        \draw (164,140.4) node [anchor=north west][inner sep=0.75pt]    {$\Phi _{2}$};
        % Text Node
        \draw (203,141.4) node [anchor=north west][inner sep=0.75pt]    {$\Phi _{3}$};
        \end{tikzpicture}
\end{center}
If we change this to a scattering diagram, and compute the large-z behavior
\begin{figure}
    \centering
\begin{minipage}{0.4\textwidth}

@@

\end{minipage}
\hspace{1em}
\begin{minipage}{0.4\textwidth}
    \begin{equation*}
        \sim 1/z^{\textcolor{red}{\textcircled{\textcolor{black}{4}}}}
    \end{equation*}
\end{minipage}
\end{figure}
\end{frame}
\section{Scattering amplitudes from BCFW}
\begin{frame}
    \frametitle{Classification of scattering amplitude}
    For the simplicity, we started front the two-site gauge theory, means that there are only two gauge fields $V_1$, $V_2$ and one scalar field $\Phi$, $\Phi^\dagger$.
    The amplitudes in this theory can be classified to many types
    \begin{columns}[T]
        \begin{column}{0.48\textwidth}
            \begin{itemize}
                \item 3-point
                    \begin{itemize}
                        \item $\bm{V_1\Phi\Phi^\dagger}$
                        \item $\bm{V_2\Phi\Phi^\dagger}$
                        \item $\bm{V_1V_1V_1}$
                        \item $\bm{V_2V_2V_2}$
                    \end{itemize}
            \end{itemize}
        \end{column}
        \begin{column}{0.48\textwidth}
            \begin{itemize}
                \item 4-point
                \begin{itemize}
                    \item $\bm{V_1V_1V_1V_1}$
                    \item $\bm{V_2V_2V_2V_2}$
                    \item $\bm{\Phi^\dagger V_1V_1\Phi}$
                    \item $\bm{\Phi V_2V_2\Phi^\dagger}$
                    \item $\bm{\Phi V_2 \Phi^\dagger V_1}$
                    \item $\bm{\Phi\Phi^\dagger\Phi\Phi^\dagger}$
                \end{itemize}
            \end{itemize}
        \end{column}
    \end{columns}
\end{frame}

\begin{frame}
    \begin{columns}[T]
        \begin{column}{0.6\textwidth}
        \begin{itemize}
            \item 5-point
            \begin{itemize}
                \item $\bm{V_1V_1V_1V_1V_1}$
                \item $\bm{V_2V_2V_2V_2V_2}$
                \item $\bm{\Phi^\dagger V_1V_1V_1\Phi}$
                \item $\bm{\Phi V_2V_2V_2\Phi^\dagger}$
                \item $\bm{V_2\Phi^\dagger V_1V_1\Phi}$
                \item $\bm{\Phi V_2V_2\Phi^\dagger V_1}$
                \item $\textcolor{red}{\Phi\Phi^\dagger\Phi\Phi^\dagger V_1}$ (Not yet solved)
                \item $\textcolor{red}{\Phi\Phi^\dagger\Phi\Phi^\dagger V_2}$ (Not yet solved)
            \end{itemize}
        \end{itemize}
    \end{column}
    \begin{column}{0.48\textwidth}
        \begin{itemize}
            \item 6-point
            \begin{itemize}
                \item $\bm{V_1V_1V_1V_1V_1V_1}$
                \item $\bm{V_2V_2V_2V_2V_2V_2}$
                \item $\bm{\Phi^\dagger V_1V_1V_1V_1\Phi}$
                \item $\bm{\Phi V_2V_2V_2V_2\Phi^\dagger}$
                \item $\bm{V_2V_2\Phi^\dagger V_1V_1\Phi}$
                \item $\bm{\Phi V_2V_2\Phi^\dagger V_1V_1}$\\
                $\qquad$ $\vdots$\\
                $\qquad$ $ \vdots$
            \end{itemize}
        \end{itemize}
    \end{column}
    \end{columns}
\end{frame}
\begin{frame}
    \frametitle{Basic building block -- 3-point}
    From the previous section, we have known that there are only two kinds of 3 point amplitude
    \begin{gather*}
        A[1,2,3^+]=\frac{[23][31]}{[12]},\qquad A[1,2,3^-]=\frac{\avg{23}\!\avg{31}}{\avg{12}}\\
        A[3^+,4^+,5^-]=\frac{[34]^3}{[45][53]},\qquad A[3^-,4^-,5^+]=\frac{\avg{34}^3}{\avg{45}\!\avg{53}}
    \end{gather*}
    By using the 3 point building block, we can construct 4 point color-ordered amplitudes from BCFW recursion relation.
\end{frame}
\begin{frame}
    \frametitle{Gauge boson sector}
    \begin{itemize}
        \item n$ V_1$ or n$V_2$\\
        This part is completely the same as the pure gluon amplitude, so we can directly borrow the
        existing results.
        \begin{equation*}
            \boxed{\text{Parke - Talyor Formula}:\quad A[\cdots,i^-,\cdots,j^-,\cdots]=\frac{\avg{ij}^4}{\avg{12}\!\avg{23}\cdots\avg{n1}}}
        \end{equation*}
        \textcolor{red}{Notice that this formula only applies for MHV amplitudes, although the NMHV can be completely solved.}
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{QCD like sector}
    \begin{itemize}
        \item $\Phi^\dagger V_1V_1\Phi$\\
        Here we compute the color-ordered amplitude $A[1,2,3^+,4^-]$. We choose $[2,3\rangle$ shift
        \begin{gather*}
        \hat{\sket{2}}=\sket{2}-z\sket{3},\qquad \hat{\aket{2}}=\aket{2} \\
        \hat{\sket{3}}=\sket{3},\qquad \hat{\aket{3}}=\aket{3}+z\aket{2}
        \end{gather*}
        The amplitudes can be computed 
        \begin{align*}
            A[1,2,3^+,4^-]=(-1)\frac{\avg{14}^2\avg{24}^2}{\mdavg{12}{23}\!\mdavg{34}{41}}
        \end{align*}
        \item $\Phi^\dagger V_1V_1V_1\Phi$
            \begin{equation*}
                A[1,2,3^+,4^+,5^-]=\frac{\avg{15}^2\!\avg{25}^2}{\mdavg{12}{23}\!\mdavg{34}{45}\!\avg{51}}
            \end{equation*}
    \end{itemize}
\end{frame}

\begin{frame}
    \begin{itemize}
        \item $\Phi^\dagger (nV_1)\Phi$
            \begin{equation*}
                A[1,2,\cdots,(n+2)^-]=(-1)^{n+1}\frac{\avg{1,n+2}^2\avg{2,n+2}^2}{\mdavg{12}{23}\cdots\mdavg{n+1,n+2}{n+2,1}}
            \end{equation*}
            \textcolor{red}{$\star$ Bonus relation: \begin{equation*}
                A[1,2,3^+,4^+]=0\quad \Rightarrow  \quad A[1,2,3^+,\cdots,n^+]=0 \end{equation*}}
        For the amplitude $\Phi (nV_2)\Phi^\dagger$, we can obtain nearly the same expression.
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Pure 2-site amplitude}
    \begin{itemize}
        \item $\Phi V_2 \Phi^\dagger V_1$
        \begin{equation*}
            A[1,2,3_1^+,4_2^-]=\frac{\mdavg{14}{24}}{\mdavg{13}{23}}
        \end{equation*}
        \item $\Phi V_2 \Phi^\dagger V_1V_1$
        \begin{equation*}
            A[1,2,3_1^+,4_1^+,5_2^-]=(-1)\frac{\avg{2\textcolor{green}{5}}^2\!\avg{1\textcolor{green}{5}}^2}{\textcolor{blue}{\mdavg{23}{34}\!\avg{41}}\textcolor{red}{\mdavg{25}{51}}}
        \end{equation*}
        \item $\Phi V_2V_2 \Phi^\dagger V_1V_1$
        \begin{equation*}
            A[1,2,3_1^+,4_1^+,5_2^+,6_2^-]=\frac{\avg{2\textcolor{green}{6}}^2\!\avg{1\textcolor{green}{6}}^2}{\textcolor{blue}{\mdavg{23}{34}\!\avg{41}}\!\textcolor{red}{\mdavg{25}{56}\!\avg{51}}}
        \end{equation*}

\appendix
\section{Appendix}
\begin{frame}
    \frametitle{Color structure}
    \begin{itemize}
        \item n$ V_1$ or n$V_2$\\
        This part is completely the same as the pure gluon amplitude, so we can directly borrow the
        existing results.
        \begin{equation*}
            \boxed{\text{Parke - Talyor Formula}:\quad A[\cdots,i^-,\cdots,j^-,\cdots]=\frac{\avg{ij}^4}{\avg{12}\!\avg{23}\cdots\avg{n1}}}
        \end{equation*}
        \textcolor{red}{Notice that this formula only applies for MHV amplitudes, although the NMHV can be completely solved.}
    \end{itemize}
\end{frame}

@@

\begin{frame}
    \frametitle{OPP(Order preserving permutation)}
    From the 4 point case, we have known that the relative order between gauge boson 1 and gauge boson 2 does not affect the color structure. 
    Thus, it is necessary to introduce the \textbf{OPP(Order preserving permutation)}. For example:
    \begin{equation*}
        (3_1,4_1,5_2) \quad (3_1,5_2,4_1) \quad (5_2,3_1,4_1)
    \end{equation*}
    These three permutations are different OPP for $(3_1,4_1,5_2)$, so that give us the same color factor.
\end{frame}
\begin{frame}
    \frametitle{Basic building block -- 3-point}
    From the previous section, we have known that there are only two kinds of 3 point amplitude
    \begin{gather*}
        A[1,2,3^+]=\frac{[23][31]}{[12]},\qquad A[1,2,3^-]=\frac{\avg{23}\!\avg{31}}{\avg{12}}\\
        A[3^+,4^+,5^-]=\frac{[34]^3}{[45][53]},\qquad A[3^-,4^-,5_+]=\frac{\avg{34}^3}{\avg{45}\!\avg{53}}
    \end{gather*}
    By using the 3 point building block, we can construct 4 point color-ordered amplitudes from BCFW recursion relation.
\end{frame}
